Finding Quality Issues in SKOS Vocabularies

### 2012-03-28 analysis.tex
incorporated antoines comments

% LABELING AND DOCUMENTATION ISSUES
We found labeling and documentation issues in all analyzed vocabularies. 
% Omitted or Invalid Language Tags
The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties. The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances and the LCSH vocabulary uses language tags with concepts, but not with concept schemes.
% Incomplete Language Coverage
\texttt{AGROVOC} covers 25 languages in total but no single concept is labelled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned. The reason for the high number of concepts with incomplete language coverage in \texttt{STW} is that a few concepts have labels with the private, but valid language tag \texttt{x-other}. 
% Undocumented Concepts
\texttt{Geonames} is the only vocabulary in our dataset, which has at least one documentation property assigned to all its concept. All other vocabularies have a significant number of undocumented concepts.
% Label Conflicts
We also detected possible label conflicts in half of the vocabularies. \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property. A similar example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
% Other stuff
The \texttt{Eurovoc} and \texttt{NAICS} vocabularies use SKOS-XL for its labels, which is currently not supported by qSKOS.

>>>>

% LABELING AND DOCUMENTATION ISSUES
We found labeling and documentation issues in all analyzed vocabularies. 
% Omitted or Invalid Language Tags
The \texttt{MeSH}, \texttt{PXV}, \texttt{Pressinfo}, and \texttt{LVAk} vocabularies omit language tags with their \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel} properties. The STW thesaurus doesn't use language tags with 2 \texttt{skos:definition} property instances and the LCSH vocabulary uses language tags with concepts, but not with concept schemes.
% Incomplete Language Coverage
\texttt{AGROVOC} covers 25 languages in total but no single concept is labelled in all languages, in \texttt{Meketre} all concepts have English but only some of them French labels assigned. The reason for the high number of concepts with incomplete language coverage in \texttt{STW} is that a few concepts have labels with the private, but valid language tag \texttt{x-other}. 
% Undocumented Concepts
\texttt{Geonames}, which is an ontology including a concept scheme of ``feature codes'', is the only vocabulary in our dataset, which has at least one documentation property assigned to all of its concept. All other vocabularies have a significant number of undocumented concepts.
% Label Conflicts
We also detected possible label conflicts in half of the vocabularies. \texttt{PXV}, for instance, uses the string ``primary peroxisomal enzyme deficiency'' with two concepts in the same concept scheme, but once with a \texttt{skos:prefLabel} and another time with a \texttt{skos:altLabel} property. A similar example from AGROVOC is ``sziv\'{a}rv\'{a}nyos pisztr\'{a}ng'', which is used as \texttt{skos:altLabel} with two different concepts.
% Other stuff
The \texttt{Eurovoc} and \texttt{NAICS} vocabularies use SKOS-XL for its labels, which is currently not supported by qSKOS.
